Macroscopic Salt Rejection through Electrostatically Gated Porous Graphene

### 2019-01-15 paper/SI.tex
Apply changes to SI Roman

Next we seek the value between $R_{\mathrm{PCTE}}$ and
$R_{\mathrm{G}}^{0}$ (ungated resistance of PG), $\delta$. It is
pointed out that the scaling laws for $R_{\mathrm{PCTE}}$ and
$R_{\mathrm{G}}^{0}$ differ. For a long channel like PCTE, the
resistance is derived from Fick's law as\cite{O_Hern_2014}:
\begin{equation}
\label{eq:R-PCTE}
 R_{\mathrm{PCTE}} = \frac{1}{D} \frac{L}{\pi r_{\mathrm{PCTE}}^{2}}
\end{equation}
whereas $D$ is the diffusivity of the species, $L$ is the length of
channel ($\sim$24 $\mathrm{\mu}$m), and $r_{\mathrm{PCTE}}$ is the
average radius of the PCTE channels ($\sim$200 nm). On the other hand,
the transport through 2D pore with high radius/thickness ratio falls
into the regime of the Sampson formula \cite{Roscoe_1949}, where the
entrance resistance dominates over the bulk resistance, with the
formula as \cite{Roscoe_1949,Celebi_2014}:
\begin{equation}
  \label{eq:sampson}
  R_{\mathrm{g}}^{0} = \frac{1}{D} \frac{3 \pi}{r_{\mathrm{G}}}
\end{equation}
We therefore estimate the value of $\delta$ as:
\begin{equation}
  \label{eq:delta-resistance}
  \delta
  = \frac{R_{\mathrm{PCTE}}}{R_{\mathrm{G}}^{0}}
  = {\displaystyle
    \frac{{\displaystyle \frac{L}
        {\pi r_{\mathrm{PCTE}}^{2}}}}
    {{\displaystyle \frac{3 \pi}{r_{\mathrm{G}}} \frac{1}{\gamma}}}}
  \approx 2.20
\end{equation}
Alternatively, we may also estimate the range of $\delta$ from
experimental data in main text \Fig{} \ref{main-fig:2}b using the
relation:
\begin{equation}
  \label{eq:exp-delta}
  \delta = \left(\frac{\boldsymbol{J}_{\mathrm{PCTE}}}{\boldsymbol{J}_{\mathrm{PG}}^{0}} -1 \right)^{-1}
\end{equation}
by assuming the validity of the circuit analog model for all salt
systems. We find that the $\delta$ value estimated from the simple
geometric model agrees well with the experimental results. As shown in
\Fig{} \ref{}, the theoretical estimated value of $\delta$ (orange
line) lies within the margin of the majority of experimental data,
which is exceptionally good given the simplicity of the model used.

@@

\section{Conductivity and Debye length for all salts}
\label{sec:salts}
In Table \ref{tab:debye}, the conductivities and calculated Debye
lengths for 6 salts are shown. At the same concentration, the higher
ionic strength of the multivalent salts leads to a reduction of the
respective Debye lengths.

>>>>

Next we seek the value between $R_{\mathrm{PCTE}}$ and
$R_{\mathrm{G}}^{0}$ (ungated resistance of PG), $\delta$. It is
pointed out that the scaling laws for $R_{\mathrm{PCTE}}$ and
$R_{\mathrm{G}}^{0}$ differ. For a long channel like PCTE, the
resistance is derived from Fick's law as\cite{O_Hern_2014}:
\begin{equation}
\label{eq:R-PCTE}
 R_{\mathrm{PCTE}} = \frac{1}{D} \frac{L}{\pi r_{\mathrm{PCTE}}^{2}}
\end{equation}
whereas $D$ is the diffusivity of the species, $L$ is the length of
channel ($\sim$24 $\mathrm{\mu}$m), and $r_{\mathrm{PCTE}}$ is the
average radius of the PCTE channels ($\sim$200 nm). On the other hand,
the transport through 2D pore with high radius/thickness ratio falls
into the regime of the Sampson formula \cite{Roscoe_1949}, where the
entrance resistance dominates over the bulk resistance, with the
formula as \cite{Roscoe_1949,Celebi_2014}:
\begin{equation}
  \label{eq:sampson}
  R_{\mathrm{g}}^{0} = \frac{1}{D} \frac{3 \pi}{r_{\mathrm{G}}}
\end{equation}
We therefore estimate the value of $\delta$ as:
\begin{equation}
  \label{eq:delta-resistance}
  \delta
  = \frac{R_{\mathrm{PCTE}}}{R_{\mathrm{G}}^{0}}
  = {\displaystyle
    \frac{{\displaystyle \frac{L}
        {\pi r_{\mathrm{PCTE}}^{2}}}}
    {{\displaystyle \frac{3 \pi}{r_{\mathrm{G}}} \frac{1}{\gamma}}}}
  \approx 2.20
\end{equation}
Alternatively, we may also estimate the range of $\delta$ from
experimental data in main text \Fig{} \ref{main-fig:2}b using the
relation:
\begin{equation}
  \label{eq:exp-delta}
  \delta = \left(\frac{\boldsymbol{J}_{\mathrm{PCTE}}}{\boldsymbol{J}_{\mathrm{PG}}^{0}} -1 \right)^{-1}
\end{equation}
by assuming the validity of the circuit analog model for all salt
systems. We find that the $\delta$ value estimated from the simple
geometric model agrees well with the experimental results. As shown in
\Fig{} \ref{fig:delta-compare}, the theoretical estimated value of $\delta$ (orange
line) lies within the margin of the majority of experimental data,
which is exceptionally good given the simplicity of the model used.

@@

\section{Conductivity and Debye length for all salts}
\label{sec:salts}
In Table \ref{tab:conductivity}, the conductivities and calculated Debye
lengths for 6 salts are shown. At the same concentration, the higher
ionic strength of the multivalent salts leads to a reduction of the
respective Debye lengths.
